% ----------------------------------------------------
% Recommendations
% ----------------------------------------------------
\documentclass[class=report,11pt,crop=false]{standalone}
\input{../Style/ChapterStyle.tex}
\input{../FrontMatter/Glossary.tex}
\begin{document}
% ----------------------------------------------------
\chapter{Recommendations \label{ch:recommendations}}
\epigraph{It is for us the living, rather, to be dedicated here to the unfinished work which they who fought here have thus far so nobly advanced.}%
    {\emph{---Abraham Lincoln}}
\vspace{0.5cm}
% ----------------------------------------------------

The nature of this short project has left many interesting and important aspects of the topic unaddressed. It is hoped that the cursory work completed here will act as a trampoline for future investigations. The recommendations for further study are summarised briefly below.

\section{\glsentrytext{dab} Processing Chain}
\begin{itemize}
    \item The use of the other three \gls{dab} transmission modes should be investigated and tested.
    \item Frequency synchronisation methods should be considered and implemented into the existing \gls{dab} processing blocks.
    \item The built-in error correction techniques of the \gls{dab} signal should be further explored and applied to real-world data.
    \item The designed \textsc{Matlab} code should be ported into a language appropriate for real-time implementation, such as \textsc{C++}, and this code should be optimised where possible. Much more work can be done in considering the efficiency of the algorithms and indivudal sub-blocks too.
    \item The entire processing chain should be adapted to allow for live streaming of \gls{dab} data, rather than simply reading from a pre-recorded binary file.
\end{itemize}

\section{Real-world Passive Radar Integration}
\begin{itemize}
    \item The \gls{dab} processing blocks should be integrated into an actual \gls{pr} processing system.
    \item The \gls{pr} system should then be tested with regards to effiency, accuracy, and similar metrics, with and without the various \gls{dab} processing techniques and blocks.
\end{itemize}





% ----------------------------------------------------
\ifstandalone
\bibliography{../Bibliography/References.bib}
\printnoidxglossary[type=\acronymtype,nonumberlist]
\fi
\end{document}
% ----------------------------------------------------