\documentclass[class=report,11pt,crop=false]{standalone}
\input{../Style/ChapterStyle.tex}
\input{../FrontMatter/Glossary.tex}
\begin{document}


% \afterpage{
% \newgeometry{margin=30mm}
\chapter*{Abstract}

\gls{pr} is a variant of radar technology in which no dedicated transmitter is required for operation. Instead, \gls{pr} systems use so-called \gls{ioo}---such as existing radio-station broadcasts---for the detection of objects in a scene. In the past decade, there has been an increased interest in the use of \emph{digital} broadcasting signals as \gls{ioo}s, as these signals offer a variety of benefits in a \gls{pr} context. One of the digital broadcasting standards that has garnered attention for use in \gls{pr} is the \gls{dab} format, which is slowly being adopted around the world to replace the antiquated analogue-modes of audio-broadcasting.

The aim of this project was to research, design, and implement a \gls{dab} processing chain, with the intention that it eventually be integrated into a \gls{pr} system. Though prior work has been done on \gls{dab}-based \gls{pr} implementations, the literature lacks a clear description of the \gls{dab} pipeline used for such scenarios. Moreover, the work that covers \gls{dab} signals more comprehensively focuses too much on the intricacies of the \gls{dab} standard, in a way that is unnecessarily complex for \gls{pr} applications. Therefore, there is a need for a clear and thorough exposition of the design procedure for a \gls{dab} processing chain, specifically within the context of \gls{pr}.

This report aims to document the project's design steps, and its associated results. After a brief surveillance of the available literature, a comprehensive consideration of the relevant aspects of the \gls{dab} standard is provided, including the key theoretical concepts that underpin it---namely, \gls{cofdm} and \gls{dqpsk}. Thereafter, a detailed unpacking of the designed \gls{dab} processing chain is provided, starting from a high-level overview, and then zooming in to the individual functional blocks. The \gls{dab} chain is then validated via several testing procedures, and is shown to pass all of them. It is thus concluded that the designed processing chain indeed works.

\ifstandalone
% \bibliography{../Bibliography/References.bib}
% \printnoidxglossary[type=\acronymtype,nonumberlist]
\fi
\end{document}