\documentclass[class=report,11pt,crop=false]{standalone}
\input{../Style/ChapterStyle.tex}
\begin{document}

\chapter*{Acknowledgements}
\epigraph{No man is an island entire of itself; every man is a piece of the continent, a part of the main.}%
    {\emph{---John Donne}}
\vspace{0.3cm}

This project---and the degree that it concludes---could not have been completed without the love and support received along the way. I am incredibly privileged and I feel overwhelmingly blessed. I wish to thank \emph{all} of those who have been a part of the journey, regardless of the role played. Nonetheless, some special notes of appreciation are due.

% Financial
Firstly, to the wonderful benefactors that have enabled me to embark on this university experience---the Allan Gray Orbis Foundation, the Klaus-J\"urgen Bathe Leadership Scholarship, PricewaterhouseCoopers South Africa, Peralex Electronics, and the UCT Engineering Faculty: thank you for your faith in me, and for your unending generosity.

% Academic
To my supervisor, Dr Stephen Paine: thank you for your patience and wisdom during this project, and for your willingness to help---even in the late hours of the night.

To Mark Cammidge: thank you for all of your assistance over the years. Thank you, too, for meticulously proofreading this report so cheerfully.

To my passionate lecturers at UCT, and my equally-passionate teachers back at Fish Hoek High School: thank you for dedicating so much of your time and energy for my sake. Thank you for inspiring me, challenging me, and helping me grow.

% Friends
To my wonderful and caring friends: Nic, thank you for the deep friendship we share. Kate, thank you for the constant support and encouragement you so readily provide to me---your companionship has made this tough year more bearable. Matt, thank you for your quirky sense of humour, which makes my life brighter. Tom, Justin, and everyone else---thank you for being an integral part of this tumultuous yet gratifying escapade.

To my lift-club partner, Mark Keeling: thank you for the hours and hours that we shared in commute, and the many kilometres we added to your car's odometer.

% Family
To my loving family: Mom and Dad, thank you for the innumerable sacrifices you have made for me, without a hint of complaint. Your unwavering support has been the bedrock of my life. Gran and Papa, thank you for your love and unceasing kindness. My dear siblings---Bron and Hennie, Jes and Dave---thank you for being some of my closest friends with whom I can enjoy life. My second family---Claire, Sara, Omi---thank you for welcoming me into your lives so graciously.

% Gem
Finally, to my best friend, Gemma: thank you for all the adventures we have shared, and for the love you continue to show me. Thank you for teaching me so much about the world.

\end{document}